---
output: md_document
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
  version.github <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])
  version.github <- gsub('-', '.', version.github)
  version.cran <- ""
  # get the version from the CRAN package mirror
  # cran.dcf.con <- url("https://raw.githubusercontent.com/cran/SAMBA/master/DESCRIPTION")
  # version.cran <- read.dcf(file = cran.dcf.con)[, "Version"]
  # close(cran.dcf.con)
  if (version.cran == version.github) {
      color <- "success"
  } else {
      color <- "informational"
  }


```
<!-- badges: start -->
[![Github Version](https://img.shields.io/badge/Github-`r version.github`-`r color`.svg?style=flat)](commits/master)
[![Travis CI](https://travis-ci.org/umich-cphds/SAMBA.svg?branch=master)](https://travis-ci.org/umich-cphds/SAMBA)
<!-- badges: end -->

# SAMBA
Health research using data from electronic health records (EHR) has gained
popularity, but misclassification of EHR-derived disease status and lack of
representativeness of the study sample can result in substantial bias in
effect estimates and can impact power and type I error for association
tests. Here, the assumed target of inference is the relationship between
binary disease status and predictors modeled using a logistic regression
model. SAMBA implements several methods for obtaining bias-corrected
point estimates along with valid standard errors as proposed in Beesley and
Mukherjee (2020), currently under review.

# Installation
`SAMBA` can be downloaded from Github via the R Package `devtools`
```{r, eval = F}
devtools::install_github("umich-cphds/SAMBA", build_opts = c())
```

# Vignette
Once you have `SAMBA` installed, you can type
```r
vignette("UsingSAMBA")
```
in R to bring up a tutorial on `SAMBA` and how to use it.

# Questions
For questions and comments about the implementation, please contact Alexander
Rix (alexrix@umich.edu). For questions about the method, contact Lauren Beesley
(lbeesley@umich.edu).

# Reference
Statistical inference for association studies using electronic health records:
handling both selection bias and outcome misclassification
Lauren J Beesley, Bhramar Mukherjee
medRxiv [2019.12.26.19015859](https://doi.org/10.1101/2019.12.26.19015859)
